ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-17 JeS_fields.tex
Update JeS_fields.tex
General plan suggestion for summary
Anna update

@@

para on implications (500 chars)

>>>>

Concern about domestic abuse is widespread, and it is rightly identified as a serious issue. However, the true severity is still often underestimated, and hard to comprehend: Of all women murdered in the UK, 41% die as a direct result of domestic abuse.

@@

para on implications (500 chars)
Our work will have implications for the police and policy-makers. The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious cases, and times of the year when the number of reported cases is likely to be higher. Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, and better understand its far-reaching societal implications (effect on socio-economic characteristics, knife crime).
